Exception Handling Bug Hazards in Android

### 2016-04-20 SPRINGER_JOURNAL/msr_journal.tex
including another limitation for the exploratory survey

\emph{\textbf{Runtime Exception wrapping a Checked Exception.}}
This wrapping was responsible for 49.5\% of
the cross-type wrappings.  From this set 50\%  were performed by methods defined by the Android platform.
We observe that this is a common implementation practice in the methods of the Android platform.
According to Java best practices checked exceptions represent conditions from which the caller
is expected to recover. By converting a checked exception in a general Runtime class,
besides loosing contextual information about the exception,
the client can simply ignore such exception - which can negatively impact the app robustness.
\textcolor{red}{Although it is considered a bad practice, when such wrapping is accompained with a well defined
exception handling policy (which assures that proper handling will be provided within the app)
the impact on app robustness can be mitigated.}

@@

Table~\ref{tab:exampeswrap} presents examples of exceptions that
were actually wrapped in this code snippet: java.lang.RuntimeException wrapped
an java.lang.OutOfMemoryError and a java.lang.StackOverflowError.
\textcolor{red}{Such Errors result from failures detected by the runtime environment which indicate
resource deficiencies from which the program cannot possibly recover.
Hence, ``hiding" an unrecoverable condition into a runtime exception
can lead to a scenario where the developer tries to handle such an exception, leading the program
to an unpredictable state. This kind of wrapping should be avoided, since it represents a
serious bug hazard.}

@@

\emph{\textbf{Checked Exception wrapping an Error.}} Most of these wrappings
 were also caused by the reflection library used by applications' methods. The methods responsible for the wrappings
were also native methods written in C. Table~\ref{tab:exampeswrap} illustrates
some of these wrappings --- some of them are masking an OutOfMemoryError
into a checked exception.
\textcolor{red}{On the one hand, by confronting the API user with a checked exception,
the API designer is forcing the client to handle the exceptional condition.
On the other hand, according to the Java specification Errors are not supposed to be
caught. In this case, even if the exception is caught by a handler, the problem 
that trigged the Error remains: there is not enough memory to execute the app.
This kind of wrapping is even more dangerous than the previous one
and may lead to the ``exception confusion'' described next.}

@@

\textcolor{red}{As previously mentioned, the goal of this work is to obtain a thorough understanding of common exception handling \emph{bug hazards} that app developers face. In the first phase of this work, we conducted a mining study which identified common exception handling bug hazards in app development.
 In the second phase of this work, we set up an exploratory qualitative investigation and surveyed Android developers on how they perceive the bug hazards detected in the mining study. The scope of our study is GitHub---using our GHTorrent database~\cite{Gousi13}, we aimed our survey at developers from Android projects available in GitHub for which issues were mined during the first phase of this study. Next sections detail this exploratory qualitative investigation.}

%\textcolor{red}{The survey mixed Liket-scale with open-ended questions, and the motivations behind the survey questions are twofold: (i) to learn from
%developers about the usage of the exception handling code in app development;  and (ii) to get developers percerptions about the bug hazards detected in
%the first phase of this study.}

%Our main goal is to learn from developers about the Java exception handling usage and the main
%exception handling bug hazards in Android. We therefore use a survey as our main research
%instrument. The survey mixed  Liket-scale with open-ended questions. The questions were motivated
%by the analysis of the existing bug hazards detected in the first phase of this study.
%The next sections detail the survey.
%Our main findings reveal that developers often handle exceptions while developing Android apps and
%we provide insights into the main challenges faced by them during this task. xxxxxxx

\subsection{Research Questions}

\textcolor{red}{The overall research question guiding our exploratory survey is
the following:
\emph{RQ 2: How do developers deal with the exception handling code in Android apps and what are the developers' perspectives about the main bug hazards found during the mining study?} This general research question has been broken into a set of research questions that are answered by the exploratory survey.}

@@

\textcolor{red}{To make the analysis easier, we further refine this question into sub-questions, as follows. To investigate whether the development of exception handling code is a daily concern for developers or it is something that developers rarely face and for that reason do not care much, the following subquestions are added: \emph{How often do developers handle exceptions?} \emph{How often do developers throw exceptions?} And, to evaluate developers knowledge concerning EH best practices, we also investigated: \emph{Do developers know about Java EH best practices and/or Android specific EH best practices?}}

@@

\textcolor{red}{Our last research question addresses whether the exception handling code helps with the development of robust Android applications, and what developers usually do to prevent apps from crashing. The motivation behind this question was to discover common practices for dealing with uncaught exceptions and to acess developers opinion about the role of the exception handling mechanism in the development of robust apps. Hence, the last question is as follows:}

@@

\textcolor{red}{Given the exploratory nature of our research, we used methods from Grounded Theory ~\cite{charmaz2006} to answer some of our research questions. Since our aim is to learn from a large number of developers, we use surveys which are known to scale well. The survey is split into two logical sections; the motivations behind each logical section are: (i) questions aiming at learning from developers about the usage of the exception handling code in app development;  and (ii) questions focusing on getting developers' perceptions about the bug hazards detected in the first phase of this study.}

\textcolor{red}{The survey comprises multiple choice or Likert-scale questions and open-ended questions. The multiple choice questions are intermixed with open-ended questions to further elicit the developer's opinions. Moreover, the survey also contains Likert-scale questions to force participants to make a choice. Overall, the survey includes 13 open-ended questions, 5 Likert-scale questions and 10 multiple choice questions. The respondents could complete the survey in about 15 minutes.}

\textcolor{red}{We used grounded theory coding to iterate through the open-ended survey responses. The grounded theory coding used in this study consists of two phases: (1) initial coding entails a close reading of the data and (2) later we used focused coding ~\cite{charmaz2006} to pinpoint and develop the most salient themes ~\cite{charmaz2006} in the analyzed data. Answers to different questions in the survey were coded separately. For all open-ended questions in the survey, coding was done by two researchers until saturation was reached. Disagreements were discussed and resolved as part of the coding, thus, we are unable to report level of agreement. In all cases, the first author was one of the two coders, and one of the other authors coded the data as well in close collaboration with the first author until saturation was reached. The first author then went through the remaining responses to assign codes to responses.}

@@

%~\cite{coelhoetal15}
 In the first phase of this study, described previously, we mined exception stack traces available in issues reported for several Android projects hosted on GitHub and Google Code. To ensure that our sample consists of repositories that were real Android apps, we had to inspect every project site and discard toy-programs and non-Android repositories. For each repository, we extract the developers whose emails are registered. We emailed the 1,824 developers and received 71 valid answers. \textcolor{red}{The response rate was 3.9\% --
although the response rate achieved in our study is low, it is in line with similar surveys reported in the literature (e.g., ~\cite{kochhar2015understanding,joorabchi2013real,bavota2015impact,ko2007information,hindle2015topics}) whose response rates mostly vary between 2\% and 4\%.}
The majority of our respondents have more than 2 years of Java development experience (87.3\%) and of Android development (85.9\%) -- see Figure~\ref{fig:devexpertise}.

@@

%\emph{EH Best Practices}
%/////// JAVA BEST PRACTICES //////
As mentioned before several general guidelines have been proposed on how to
use Java exceptions. Section~\ref{sec:best}  compiled a list of some exception
handling (EH) best practices that guided our mining study. In this survey the
developers were also asked if they knew about and used Java EH best practices --
see Figure~\ref{fig:allquest}. Most of them said that they knew and adopted Java
EH practices (68\%). From this set the most mentioned best practices are
presented in Table~\ref{tab:javapractices} -- considering that one developer
mentioned more than one practice. Most of the best practices mentioned were the
ones cited in Section~\ref{sec:best}. For instance:\emph{``Don't throw [pure]
RuntimeException (in most cases), don't catch OutOfMemoryError, etc." [D42]}.
Some of the practices mentioned, however, are not well known Java EH best
practices but seem to be used by some Android developers to better deal with
exceptions in the Android app context, such as the use of a crash fast
approach\footnote{\url{http://www.slideshare.net/pyricau/crash-fast}} --
\emph{``Crash is good for hinting developer. Fast crash fast solve." [D51]}.
\textcolor{red}{According to this approach, developers should let the
application crash as soon as an unexpected situation happens. The motivation
behind this approach is that the developer will receive the crash information
and fix the potential bug that caused it. On the other hand, if the developer
lets the app continue to run after an exception had happened, the
application may enter an inconsistent state. In such scenario, the time between the fault being exercised and the failure (the fault manifestation) increases, which may impair finding and fixing the potential bug that caused the failure.} Moreover, some respondents favor checked exceptions instead of runtime to represent the exceptional conditions in Android apps -- \emph{``RuntimeExceptions are not particularly well suited for Android's robustness, as any uncaught one would cause a crash." [D26]}; \emph{``Checked exception help, unchecked exceptions don't." [D25]}; \emph{``avoid unchecked exceptions except if the case is really abnormal and should not happen [...]"[D45]}.

@@

\textcolor{red}{This section discusses the lessons learned from the mining and the survey studies. The mining study revealed a set of bug
hazards -- such as (i) the cross-type wrappings; (ii) the abundance of null pointer problems; and (iii) the undocumented runtime
exceptions signaled by third-party code, which were confirmed by developers
during the survey. Here, we discuss the identified bug hazards, we present how
the developers perceived them and point out at what developers can do in
order to deal with them.}

@@

\textcolor{red}{The process for
identifying the type of exceptions reported in stack traces may not be completely
accurate.
Specifically, we performed the selection of the version of the exception source code or bytecode
to analyze, as follows: (i) for all exceptions signaled by the Android Platform
and the Java Environment the analysis was based on Version 4.4 of Android platform (API level 19);  (ii)
for the exceptions signaled by applications, the analysis considered
the last version of the application source-code available on Github/Google code; and (iii)
for all exceptions signaled by third-party libraries the type analysis
considered the latest bytecode version available on the app repository.
When the exception could not be found automatically or manually (based on the chosen version),
we classified the exception as ``Undefined''.  Only 31 exceptions
remained undefined, which occurred in 60 different exception stack traces out of 6,005 mined stack traces.
Hence, the exception type could not be accurately identified in 1\% of the mined
exception flows.
There should be situations where the exception type (i.e., checked or runtime) changes from one version to another.
Although we believe that it will not happen very often, we did not investigate
this issue.}

@@

\subsection{Limitations of the Survey-based Study}
Due to the exploratory nature of the second phase of this work whose
goal was to identify the developers' perspectives concerning the exception
handling bug hazards found during the repository mining
phase, we chose Grounded Theory techniques. The results of our
survey-based study may not apply to every Android developer, since other populations
might add new insights.  The population we collected data from was comprised
of Android developers of the GitHub
Android projects whose issues were mined in the first phase of this work, and who had
time and motivation to answer the survey questions.

Although the themes and findings that emerged in our study cannot
be generalized, they give a first view of developers' perspectives about
 EH bug hazards found. Hence, we believe that the survey-based study
has contributed with valuable insights about how Android developers
used the exception handling code and what their perspectives regarding
exception handling bug hazards are.

@@

\textcolor{red}{Exploratory surveys have also targeted Android developers~\cite{kochhar2015understanding,joorabchi2013real,bavota2015impact,linares2015developers}.
Kochhar et al. ~\cite{kochhar2015understanding} conducted a survey-based study to discover the
commonly used tools for mobile app testing as well as the problems
faced by developers while testing the apps. The survey was sent to 3,905 emails of Android developers
and received 83 responses (response rate of 2.13\%).
Joorabchi et al. ~\cite{joorabchi2013real} performed a survey-based study whose goal was to better understand the main challenges
developers face when building apps for different mobile devices.
They interviewed 12 senior mobile developers and performed a semi-structured survey, with 188 respondents
 from the mobile development community, since the survey was shared via e-mail groups and social media websites
response rate of the survey could not be calculated. Linares-V\'{a}squez et al. ~\cite{linares2015developers} surveyed 485 open source Android
app and library developers (for projects hosted on GitHub)  to understand developers' practices for detecting and fixing
performance bottlenecks in mobile apps.  This work emailed the survey to 24,340 developers and received
628 responses - the response rate was 2.6\%.
Bavota et al. ~\cite{bavota2015impact} investigated the impact of API change-proness and fault-proneness on the user ratings of Android apps.
They surveyed developers to assess their perspective on whether such problems could be the cause for unfavorable user ratings.
The response rate was 4\%.
A common characteristic among such works and our work is the low response rate of the surveys (between 4\% and 2\%).
None of these surveys, however, assessed how developers deal with exceptions in Android nor
the developers' perspective regarding a set of exception handling bug hazards.
In our study,
we conduced the first exploratory survey focusing on exception handling issues in Android development.}

>>>>

\emph{\textbf{Runtime Exception wrapping a Checked Exception.}}
This wrapping was responsible for 49.5\% of
the cross-type wrappings.  From this set 50\%  were performed by methods defined by the Android platform.
We observe that this is a common implementation practice in the methods of the Android platform.
According to Java best practices checked exceptions represent conditions from which the caller
is expected to recover. By converting a checked exception in a general Runtime class,
besides loosing contextual information about the exception,
the client can simply ignore such exception - which can negatively impact the app robustness.
Although it is considered a bad practice, when such wrapping is accompained with a well defined
exception handling policy (which assures that proper handling will be provided within the app)
the impact on app robustness can be mitigated.
%\textcolor{red}

@@

Table~\ref{tab:exampeswrap} presents examples of exceptions that
were actually wrapped in this code snippet: java.lang.RuntimeException wrapped
an java.lang.OutOfMemoryError and a java.lang.StackOverflowError.
Such Errors result from failures detected by the runtime environment which indicate
resource deficiencies from which the program cannot possibly recover.
Hence, ``hiding" an unrecoverable condition into a runtime exception
can lead to a scenario where the developer tries to handle such an exception, leading the program
to an unpredictable state. This kind of wrapping should be avoided, since it represents a
serious bug hazard.
%\textcolor{red}

@@

\emph{\textbf{Checked Exception wrapping an Error.}} Most of these wrappings
 were also caused by the reflection library used by applications' methods. The methods responsible for the wrappings
were also native methods written in C. Table~\ref{tab:exampeswrap} illustrates
some of these wrappings --- some of them are masking an OutOfMemoryError
into a checked exception.
{On the one hand, by confronting the API user with a checked exception,
the API designer is forcing the client to handle the exceptional condition.
On the other hand, according to the Java specification Errors are not supposed to be
caught. In this case, even if the exception is caught by a handler, the problem 
that trigged the Error remains: there is not enough memory to execute the app.
This kind of wrapping is even more dangerous than the previous one
and may lead to the ``exception confusion'' described next.
%\textcolor{red}

@@

As previously mentioned, the goal of this work is to obtain a thorough understanding of common exception handling \emph{bug hazards} that app developers face. In the first phase of this work, we conducted a mining study which identified common exception handling bug hazards in app development.
 In the second phase of this work, we set up an exploratory qualitative investigation and surveyed Android developers on how they perceive the bug hazards detected in the mining study. The scope of our study is GitHub---using our GHTorrent database~\cite{Gousi13}, we aimed our survey at developers from Android projects available in GitHub for which issues were mined during the first phase of this study. Next sections detail this exploratory qualitative investigation.
%\textcolor{red}

\subsection{Research Questions}
%\textcolor{red}
The overall research question guiding our exploratory survey is
the following:
\emph{RQ 2: How do developers deal with the exception handling code in Android apps and what are the developers' perspectives about the main bug hazards found during the mining study?} This general research question has been broken into a set of research questions that are answered by the exploratory survey.

@@

%\textcolor{red}
To make the analysis easier, we further refine this question into sub-questions, as follows. To investigate whether the development of exception handling code is a daily concern for developers or it is something that developers rarely face and for that reason do not care much, the following subquestions are added: \emph{How often do developers handle exceptions?} \emph{How often do developers throw exceptions?} And, to evaluate developers knowledge concerning EH best practices, we also investigated: \emph{Do developers know about Java EH best practices and/or Android specific EH best practices?}

@@

%\textcolor{red}
Our last research question addresses whether the exception handling code helps with the development of robust Android applications, and what developers usually do to prevent apps from crashing. The motivation behind this question was to discover common practices for dealing with uncaught exceptions and to acess developers opinion about the role of the exception handling mechanism in the development of robust apps. Hence, the last question is as follows:

@@

%\textcolor{red}
Given the exploratory nature of our research, we used methods from Grounded Theory ~\cite{charmaz2006} to answer some of our research questions. Since our aim is to learn from a large number of developers, we use surveys which are known to scale well. The survey is split into two logical sections; the motivations behind each logical section are: (i) questions aiming at learning from developers about the usage of the exception handling code in app development;  and (ii) questions focusing on getting developers' perceptions about the bug hazards detected in the first phase of this study.

%\textcolor{red}
The survey comprises multiple choice or Likert-scale questions and open-ended questions. The multiple choice questions are intermixed with open-ended questions to further elicit the developer's opinions. Moreover, the survey also contains Likert-scale questions to force participants to make a choice. Overall, the survey includes 13 open-ended questions, 5 Likert-scale questions and 10 multiple choice questions. The respondents could complete the survey in about 15 minutes.

%\textcolor{red}
We used grounded theory coding to iterate through the open-ended survey responses. The grounded theory coding used in this study consists of two phases: (1) initial coding entails a close reading of the data and (2) later we used focused coding ~\cite{charmaz2006} to pinpoint and develop the most salient themes ~\cite{charmaz2006} in the analyzed data. Answers to different questions in the survey were coded separately. For all open-ended questions in the survey, coding was done by two researchers until saturation was reached. Disagreements were discussed and resolved as part of the coding, thus, we are unable to report level of agreement. In all cases, the first author was one of the two coders, and one of the other authors coded the data as well in close collaboration with the first author until saturation was reached. The first author then went through the remaining responses to assign codes to responses.

@@

%~\cite{coelhoetal15}
%\textcolor{red}{
 In the first phase of this study, described previously, we mined exception stack traces available in issues reported for several Android projects hosted on GitHub and Google Code. To ensure that our sample consists of repositories that were real Android apps, we had to inspect every project site and discard toy-programs and non-Android repositories. For each repository, we extract the developers whose emails are registered. We emailed the 1,824 developers and received 71 valid answers. The response rate was 3.9\% --
although the response rate achieved in our study is low, it is in line with similar surveys reported in the literature (e.g., ~\cite{kochhar2015understanding,joorabchi2013real,bavota2015impact,ko2007information,hindle2015topics}) whose response rates mostly vary between 2\% and 4\%.
The majority of our respondents have more than 2 years of Java development experience (87.3\%) and of Android development (85.9\%) -- see Figure~\ref{fig:devexpertise}.

@@

%\emph{EH Best Practices}
%/////// JAVA BEST PRACTICES //////
As mentioned before several general guidelines have been proposed on how to
use Java exceptions. Section~\ref{sec:best}  compiled a list of some exception
handling (EH) best practices that guided our mining study. In this survey the
developers were also asked if they knew about and used Java EH best practices --
see Figure~\ref{fig:allquest}. Most of them said that they knew and adopted Java
EH practices (68\%). From this set the most mentioned best practices are
presented in Table~\ref{tab:javapractices} -- considering that one developer
mentioned more than one practice. Most of the best practices mentioned were the
ones cited in Section~\ref{sec:best}. For instance:\emph{``Don't throw [pure]
RuntimeException (in most cases), don't catch OutOfMemoryError, etc." [D42]}.
Some of the practices mentioned, however, are not well known Java EH best
practices but seem to be used by some Android developers to better deal with
exceptions in the Android app context, such as the use of a crash fast
approach\footnote{\url{http://www.slideshare.net/pyricau/crash-fast}} --
\emph{``Crash is good for hinting developer. Fast crash fast solve." [D51]}.
According to this approach, developers should let the
application crash as soon as an unexpected situation happens. The motivation
behind this approach is that the developer will receive the crash information
and fix the potential bug that caused it. On the other hand, if the developer
lets the app continue to run after an exception had happened, the
application may enter an inconsistent state. In such scenario, the time between the fault being exercised and the failure (the fault manifestation) increases, which may impair finding and fixing the potential bug that caused the failure. Moreover, some respondents favor checked exceptions instead of runtime to represent the exceptional conditions in Android apps -- \emph{``RuntimeExceptions are not particularly well suited for Android's robustness, as any uncaught one would cause a crash." [D26]}; \emph{``Checked exception help, unchecked exceptions don't." [D25]}; \emph{``avoid unchecked exceptions except if the case is really abnormal and should not happen [...]"[D45]}.
%\textcolor{red}

@@

This section discusses the lessons learned from the mining and the survey studies. The mining study revealed a set of bug
hazards -- such as (i) the cross-type wrappings; (ii) the abundance of null pointer problems; and (iii) the undocumented runtime
exceptions signaled by third-party code, which were confirmed by developers
during the survey. Here, we discuss the identified bug hazards, we present how
the developers perceived them and point out at what developers can do in
order to deal with them.
%\textcolor{red}{

@@

The process for
identifying the type of exceptions reported in stack traces may not be completely
accurate.
Specifically, we performed the selection of the version of the exception source code or bytecode
to analyze, as follows: (i) for all exceptions signaled by the Android Platform
and the Java Environment the analysis was based on Version 4.4 of Android platform (API level 19);  (ii)
for the exceptions signaled by applications, the analysis considered
the last version of the application source-code available on Github/Google code; and (iii)
for all exceptions signaled by third-party libraries the type analysis
considered the latest bytecode version available on the app repository.
When the exception could not be found automatically or manually (based on the chosen version),
we classified the exception as ``Undefined''.  Only 31 exceptions
remained undefined, which occurred in 60 different exception stack traces out of 6,005 mined stack traces.
Hence, the exception type could not be accurately identified in 1\% of the mined
exception flows.
There should be situations where the exception type (i.e., checked or runtime) changes from one version to another.
Although we believe that it will not happen very often, we did not investigate
this issue.
%\textcolor{red}

@@

\subsection{Limitations of the Survey-based Study}
\emph{Results Generalization.} Due to the exploratory nature of the second phase of this work whose
goal was to identify the developers' perspectives concerning the exception
handling bug hazards found during the repository mining
phase, we chose Grounded Theory techniques. The results of our
survey-based study may not apply to every Android developer, since other populations
might add new insights.  The population we collected data from was comprised
of Android developers of the GitHub
Android projects whose issues were mined in the first phase of this work, and who had
time and motivation to answer the survey questions.
Although the themes and findings that emerged in our study cannot
be generalized, they give a first view of developers' perspectives about
 EH bug hazards found. Hence, we believe that the survey-based study
has contributed with valuable insights about how Android developers
used the exception handling code and what their perspectives regarding
exception handling bug hazards are.

%I found strange that the authors did not exploit this opportunity for asking their opinion about the specific issues you identified in *their* apps. IMHO, this would provide much more qualitative feedback (while of course requiring the customisation of the survey for each specific developer). Can you please justify this choice in the paper?

\emph{Survey Customization.} Although the survey was applied to developers who had contributed to at least one of the GitHub apps, analyzed in the mining study, the survey was not customized to each developer. In other words, it did not contain questions focusing specific bug hazards identified in their apps. That customization of the survey (for each specific developer/app) could give more insights about the exception handling usage and bug hazards, and could even have improved the response rate for the survey. However, we did not followed this approach because the high number of projects analyzed (482 Android apps) and their contributors (1,824 developers) would increase the complexity and time needed (i) to customize the survey and specially (ii) to analyze the survey responses - since themes could emerge from specific contexts. This approach can be very useful in a guided interview involving some of the respondents to refine the findings of this exploratory survey, in a future work.

%TODO INCLUDE THE RESON BEHINF THE GENERAL SURVEY.

@@

Exploratory surveys have also targeted Android developers~\cite{kochhar2015understanding,joorabchi2013real,bavota2015impact,linares2015developers}.
Kochhar et al. ~\cite{kochhar2015understanding} conducted a survey-based study to discover the
commonly used tools for mobile app testing as well as the problems
faced by developers while testing the apps. The survey was sent to 3,905 emails of Android developers
and received 83 responses (response rate of 2.13\%).
Joorabchi et al. ~\cite{joorabchi2013real} performed a survey-based study whose goal was to better understand the main challenges
developers face when building apps for different mobile devices.
They interviewed 12 senior mobile developers and performed a semi-structured survey, with 188 respondents
 from the mobile development community, since the survey was shared via e-mail groups and social media websites
response rate of the survey could not be calculated. Linares-V\'{a}squez et al. ~\cite{linares2015developers} surveyed 485 open source Android
app and library developers (for projects hosted on GitHub)  to understand developers' practices for detecting and fixing
performance bottlenecks in mobile apps.  This work emailed the survey to 24,340 developers and received
628 responses - the response rate was 2.6\%.
Bavota et al. ~\cite{bavota2015impact} investigated the impact of API change-proness and fault-proneness on the user ratings of Android apps.
They surveyed developers to assess their perspective on whether such problems could be the cause for unfavorable user ratings.
The response rate was 4\%.
A common characteristic among such works and our work is the low response rate of the surveys (between 4\% and 2\%).
None of these surveys, however, assessed how developers deal with exceptions in Android nor
the developers' perspective regarding a set of exception handling bug hazards.
In our study,
we conduced the first exploratory survey focusing on exception handling issues in Android development.
%\textcolor{red}
